\begin{song}{title = It's my life, capo=3}
\capo
\end{song}

\columnratio{0.8}
\begin{paracol}{2}
\setleadsheets{title-template = empty}
\begin{song}{}
\begin{intro}
^{Am |Cm} - ^{F |G#} - ^{G |Bb} - ^{Am |Cm} - ^{F |G#} - ^{G |Bb}
\end{intro}
 
\begin{verse}
^{Am | Cm}This ain't a song for the ^{G | Bb}broken ^{F | G#}hearted, - ^{Am | Cm} - ^{F | G#} - ^{E | G} \\
no ^{Am | Cm}silent prayer for the ^{G | Bb}faith ^{F | G#}departed. - ^{Am | Cm} - ^{F | G#} - ^{E | G} \\
^{Am | Cm}I ain't gonna be just a ^{G | Bb}face in the ^{F | G#}crowd, \\
you're ^{Am | Cm}gonna hear my voice when I ^{G | Bb}shout it out ^{F | G#}loud!
\end{verse}
 
\begin{chorus}[template = framed]
^{G | Bb}It's my ^{Am | Cm}life, it's ^{F | G#}now or never, \\
^{C | D#} I ain't gonna ^{G | Bb}live forever. \\
^{Am | Cm}I just want to ^{F | G#}live while I'm ^{C | D#}alive. - ^{G | Bb} \\
It's my ^{Am | Cm}life, my heart is like an ^{F | G#}open highway, \\
^{C | D#}like Frankie said, I did ^{G | Bb}it my way. \\
^{Am | Cm}I just wanna ^{F | G#}live while I'm alive. ^{G | Bb} \\
^{F | G#}It's - ^{G | Bb}my - ^{Am | Cm}life! - ^{F | G#} - ^{E | G} - ^{Am | Cm} - ^{F | G#} - ^{E | G}
\end{chorus}
 
\begin{verse}
^{Am | Cm}This is for the ones who ^{G | Bb}stood their ^{F | G#}ground, - ^{Am | Cm} - ^{F | G#} - ^{E | G} \\
for ^{Am | Cm}Tommy and Gina who ^{G | Bb}never backed ^{F | G#}down. - ^{Am | Cm} - ^{F | G#} - ^{E | G} \\
^{Am | Cm}Tomorrow's getting harder make ^{G | Bb}no ^{F | G#}mistake, \\
^{Am | Cm}luck ain't even lucky, got to ^{G | Bb}make your own ^{F | G#}breaks. \\
^{F | G#} - ^{G | Bb} - ^{Am | Cm} - ^{F | G#} - ^{C | D#} - ^{G | Bb} - ^{Am | Cm} - ^{F | G#} - ^{C | D#} - ^{G | Bb}
\end{verse}
 
\begin{chorus}
x1
\end{chorus} 

\begin{verse}
^{Am | Cm}Better stand tall when they're ^{G | Bb}calling you ^{F | G#}out, \\
don't ^{Am | Cm}bend, don't break, baby, ^{G | Bb}don't back ^{F | G#}down! 
\end{verse}
 
\begin{chorus}
x2
\end{chorus}

\end{song}
\setleadsheets{title-template = tabular}

\chordAm
\chordF
\chordG
\chordE
\chordC

\switchcolumn

\chordCm
\\ ~ \\

\chordGsharp
\\ ~ \\

\chordBb
\\ ~ \\

\chordDsharp
\\ ~ \\

\chordG

\vfill
\hfill
\qrcode{https://open.spotify.com/track/0v1XpBHnsbkCn7iJ9Ucr1l?si=bcede8d3335e41d5}

\end{paracol}
