\begin{song}{title = The Show must go on}
\end{song}

\columnratio{0.5}
\begin{paracol}{2}
\setleadsheets{title-template = empty}
\begin{song}{}
\begin{intro}
_{Bm}   _{G}   _{Em}   _{F#}   _{Em}
\end{intro}
 
\begin{verse}
Empty ^*{Bm}spac es - what are we living for \\
abandoned ^*{G}plac es - I guess we know the score \\
^{Em}on and on, \\
does ^*{F#}any body know what we are ^*{Em}look ing for? \\

Another ^{Bm}hero, another mindless crime \\
behind the ^*{G}cur tain, in the pantomime \\
^{Em}hold the line, \\
does ^*{F#}any body want to take it any^{Em}more?
\end{verse}
 
\begin{chorus}
x1
\end{chorus}
 
\begin{verse}
Whatever ^*{C#m}happ ens, I'll leave it all to chance \\
another ^*{A}heart ache, another failed romance \\
^{F#m}on and on, \\
does ^*{G#}any body know what we are li^{F#m}ving for? \\

I guess I'm ^*{C#m}learn ing, I must be warmer now, \\
I'll soon be ^*{A}turn ing, round the corner now \\
out^{F#m}side the dawn is breaking \\
but ^*{G#}in side in the dark I'm aching ^{F#m}to be free. ^{Em}
\end{verse}
 
\begin{chorus}
x1
\end{chorus}

\switchcolumn

\begin{solo}
| _{Bm} | _{Bm}  | _{G}   | _{G}   | \\
| _{Em}  | _{F#}  | _{Em}  |
\end{solo}

\begin{bridge}
^{F} My soul is ^*{G}paint ed \\
like the ^{Em}wings of butter^{Am}flies ^{G} \\
^*{F}Fairy tales of ^*{G}yes terday \\
will ^{Em}grow but never ^{Am}die \\
I ^{C#m7b5}can fly \tab ^{D}my ^{Dsus4}friends. ^{D}
\end{bridge}

\begin{chorus}
... I'll ^{Em}face it with a grin \\
I'm ^{F#}never giving in \\
oh ^{Em}on with the show.
\end{chorus}
 
\begin{solo}
| _{Bm}  | _{Bm}  | _{G}   | _{G} |
\end{solo}
 
\begin{outro}
I'll ^{Em}top the bill, I'll overkill, \\
^{F#}I have to find the will to carry ^{Em}on. \\
The show must go ^{Bm}on.
\end{outro}

\end{song}

\chordBm
\chordG
\chordEm

\end{paracol}

\columnratio{0.29}
\begin{paracol}{2}

\setleadsheets{title-template = empty}
\begin{song}{}
\begin{chorus}[template = framed]
The show must go ^{Bm}on, \\
the show must go ^{G}on, yeah, \\
in^{Em}side my heart is breaking \\
my ^*{F#}make up may be flaking \\
but my ^{Em}smile still ^{Bm}stays on.
\end{chorus}
\end{song}

\vfill \qrcode{https://open.spotify.com/track/5n6RDaGFSN88oRWuGtYAIN?si=216a56507df6433e}

\switchcolumn


\chordFsharp
\chordCsharpm
\chordA
\chordFsharpm
\chordGsharp
\\ ~ \\


\chordF
\chordAm
\chordCsharpmsevenbfive
\chordD
\chordDsusfour


\end{paracol}

\setleadsheets{title-template = tabular}
